Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-02-16 AO_bondedSi.tex
overhaul section on smallest gap this technique can detect

Figures \ref{figVG03full} to \ref{figVG12} show examples of the predicted and measured IR spectra.  Figure \ref{figVG03_f100} shows an example spectrum in which the measurement is consistent with the prediction for a gap with the known conditions.  Meanwhile, Figure \ref{figVG12_f50} shows a spectrum in which the measurement marginally exceeds the prediction (by about $\sim 3 \sigma$).  Other parts show less consistency with the prediction due to the difficulty of direct-bonding Si in the absence of thermal annealing.

@@

\subsection{Spatially resolved measurements with Sample Transport Accessory}
We acquired spatially resolved measurements of sample VG09-12 with the Cary 5000 sample transport accessory\verb|\ref{link-to-STA-website}|.  This accessory translates the sample through the measurement beam and takes a transmission spectrum at each position.  The 2 mm step size is comparable to the monochromator's slit size.  We sampled 50 mm across the mesh pattern and into the off-mesh pattern.  The large number of consecutive measurements prevented the requisite near-contemporaneous baseline measurements for normalization.  We fit a line to before-and-after baseline measurements to infer the mean-level drift, which we divided out of each spectrum.  We reduced the measured wavelength range to $1250-1775\;$nm.

%Figure \verb|\ref{photo-of-VG09-12}| shows an illustration of sample VG09-12, with the approximate center locations of measurements marked with colored dots.  The colored dots match the color of the spectra in Figure \verb|\ref{fig-STA-obs}| The approximate size of the measurement beam is shown for scale.  The conspicuous mesh pattern has a lab measured depth of $49\pm6\;$nm, and fill factor of 50\%.  The prediction band for a transmision spectrum with those properties, and zero extra gap is shown as the green apple colored swath.  If the mesh pattern were perfectly bonded, we would expect all the spectra to fall inside the color swath in Figure \verb|\ref{fig-STA-obs}|.  Instead we see that some spectra are inside the swath, and others show a deficit of flux, indicating an extra gap as in the mixture model in Equation \verb|\ref{mixture-model-equation}|.

Sample VG09-12 has a single coarse mesh.  The mesh is composed of boxes plasma-etched to a depth of $49\pm6\;$nm.   The boxes have an edge length of 1.5 mm.  The edges of adjacent boxes are spaced 0.62 mm apart, to yield an overall fill factor of 50\%.  The Cary5000 measurement beam size is $\sim$1 mm $\times$ 10 mm.  Since the beam size is comparable to the mesh size, the fill factor at the position of the measurement will will differ from 50\%. The slit measurement was aligned with the mesh grid.  The highest fill factor acheivable is about 75\%, assuming the slit fit perfectly within a column of boxes.  The slit is larger than 0.62 mm, so the measurement cannot exhibit a 0\% fill factor of voids.  The precise value of the minimum fill factor depends on the details of the slit width, which is not known precisely.  We assume that a minimum fill factor of 30\%, but caution that this boundary is fuzzy.  Figure \verb|\ref{VG09-12 coarse mesh STA}| shows

\begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{0.35\textwidth}
              \includegraphics[width=\textwidth]{figs/VG09_12_STA_illustration.pdf}
              \caption{Illustration of VG09-12 sample transport accessory measurement positions}
		\label{figVG12_STA_corner}
        \end{subfigure}
        \begin{subfigure}[b]{0.65\textwidth}
                \includegraphics[width=\textwidth]{figs/VG0912_STA_scan_coarse.pdf}
                \caption{Measured gap transmission spectra of VG09-12 on- and off- mesh}
                \label{figVG12_f50}
        \end{subfigure}
\caption{Predictions and measurements of the coarse mesh region in sample VG09-12.
\label{figVG12}}
\end{figure}

@@

\subsection{What is the smallest gap this technique can detect?}
We devised two experiments to approach the question, ``What is the smallest gap this technique can detect?''.  We applied our MCMC model fitting formalism to an unbonded DSP wafer.  The measured transmission spectrum was normalized by a transmission spectrum of the same sample taken only a few minutes earlier.  Any difference of this normalized transmission from unity is attributable entirely to measurement uncertainty, and represents the smallest possible signal one could extract.  We also measured bonded sample VG09-12 in a region away from the intentionally implanted gap.  This spectrum was processed in the same way as the spectra of the VG09-12 mesh area, exhibiting a mean value of 0.9998 and a standard deviation $\sigma=0.0008$.  This spectrum is consistent with no gap.  We applied our MCMC formalism to further constrain the range of gap sizes consistent with the spectrum.  Table \verb|\ref{tbl summary of gap fit extents}| summarizes the sizes of gaps.  The well-calibrated DSP noise spectrum rules out ($>3\sigma$) gap sizes larger than about 8.0 nm over $>80$\% of the measurement area.  Similarly, the VG09-12 off-mesh spectrum rules out gaps greater than 13 nm over $>80$\% of the measurement area.

The variance of individual measurement uncertainties was large enough to consider for this measurement.  So rather than assume homoscedastic uncertainty as we did for the other measurements, we estimated the heteroscedastic uncertainties in the following way.  We computed the mean-subtracted transmission for four DSP measurements bookending the those of VG02.  The DSP measurements were detrended, and the measurement-to-measurement variance computed.  The result was a variance spectrum which peaks at $1850\;$nm at 0.25\%, but with a median value equal to 0.03\%.  Figure \verb|\ref{fig_xxx}| includes the $1\;\sigma$ errorbars computed in this way.

>>>>

@@

\subsection{Spatially resolved measurements with Sample Transport Accessory}
We acquired spatially resolved measurements of sample VG09-12 with the Cary 5000 sample transport accessory \footnote{\url{http://www.chem.agilent.com/en-US/products-services/instruments-systems/molecular-spectroscopy/sample-transport-accessory/}}.  This accessory translates the sample through the measurement beam and takes a transmission spectrum at each position.  We chose a 2 mm step size, which is slightly larger than the $\sim1$ mm beam width.  We sampled 50 mm across the mesh pattern and into the off-mesh pattern (Figure \ref{figVG0912_STA_illus}).  The large number of consecutive measurements prevented the requisite near-contemporaneous baseline measurements for normalization.  We fit a line to before-and-after baseline measurements to infer the mean-level drift, which we divided out of each spectrum.  We reduced the measured wavelength range to $1250-1775\;$nm.

Figure \ref{figV09G12_STA_illus}) shows an illustration of sample VG09-12, with the approximate center locations of measurements marked with colored dots.  The colored dots match the color of the spectra in Figure \ref{figVG0912} The approximate size of the measurement beam is shown for scale.  The conspicuous mesh pattern has a lab measured depth of $49\pm6\;$nm, and global fill factor of 50\%.  However, since the beam size is comparable to mesh grid size, the achieved fill factor can vary from about 30\% to 75\%.  The gray band in Figure \ref{figVG0912} represents the allowable range of predictions, taking into account both the uncertainty in the mesh depth and fill factor.  If the mesh pattern were perfectly bonded, we would expect all the spectra to fall inside the color swath in Figure \ref{figVG0912}.  We see excellent consistency between prediction and measurement, though we cannot rule out the presence of extra gaps in the mesh area.  Outside the mesh area, the bonding is excellent, as demonstrated by the off-mesh transmission close to unity transmission.

\begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{0.35\textwidth}
              \includegraphics[width=\textwidth]{figs/VG09_12_STA_illustration.pdf}
              \caption{Illustration of VG09-12 sample transport accessory measurement positions}
		\label{figVG0912_STA_illus}
        \end{subfigure}
        \begin{subfigure}[b]{0.65\textwidth}
                \includegraphics[width=\textwidth]{figs/VG0912_STA_scan_coarse.pdf}
                \caption{Measured gap transmission spectra of VG09-12 on- and off- mesh}
                \label{figVG0912}
        \end{subfigure}
\caption{Predictions and measurements of the coarse mesh region in sample VG09-12.  We took 50 measurements across the face of VG09-12, including both on- and off- mesh regions.  The measurements are consistent with the predicted transmission, shown as the gray band.  The off-mesh regions demonstrate near-perfect bonding.
\label{figVG12}}
\end{figure}

@@

\subsection{What is the smallest gap this technique can detect?}
We devised two experiments to approach the question, ``What is the smallest gap this technique can detect?''.  We applied our MCMC model fitting formalism to an unbonded DSP wafer.  The measured transmission spectrum was normalized by a transmission spectrum of the same sample taken only a few minutes earlier.  Any difference of this normalized transmission from unity is attributable entirely to measurement uncertainty, and represents the smallest possible signal one could extract.  We also measured bonded sample VG09-12 in a region away from the intentionally implanted gap.  This spectrum was processed in the same way as the spectra of the VG09-12 mesh area, exhibiting a mean value of 0.9998 and a standard deviation $\sigma=0.0008$.  This spectrum is consistent with no gap.  We applied our MCMC formalism to further constrain the range of gap sizes consistent with the spectrum.  Table \ref{tbl_DerivedGapSizes} summarizes the sizes of gaps.  The well-calibrated DSP noise spectrum rules out (at $>3\sigma$) gap sizes larger than about 9.0 nm over $>80$\% of the measurement area.  Similarly, the VG09-12 off-mesh spectrum rules out gaps greater than 14 nm over $>80$\% of the measurement area.  Figure \ref{} shows the corner plots and spectra for the
